Structure-Preserving Model-Reduction of Dissipative Hamiltonian Systems

### 2017-03-18 dissipative_hamiltonian/chapters/3.model.tex
progress in porthamiltonian section
introduction added

\section{Model Order Reduction}
In this section we first explain the main results of \cite{Peng:2014di} regarding model reduction of Hamiltonian systems. In section ?? we introduce the model reduction of dissipative Hamiltonian systems.

@@

\subsection{Model Reduction of Dissipative Hamiltonian Systems}

@@

\begin{algorithm}
\caption{Model Reduction For Dissipative Hamiltonian Systems} \label{alg:3.1}
\begin{enumerate}
	\item Construct the Hamiltonian extension (\ref{eq:2.10.a})-(\ref{eq:2.10.c}) to the original TDD system (\ref{eq:2.4}).
	\item Collect the snapshots $z(t_i)$, $i=1,\dots,N$ through time integration of the extended Hamiltonian.
	\item Construct an ortho-symplectic basis $A$.
	\item Define $\tilde L = A^T L A$, $\tilde \chi = A^T \chi A$ and construct the reduced dissipative Hamiltonian system (\ref{eq:3.12.a})-(\ref{eq:3.12.c})
\end{enumerate}
\end{algorithm}

>>>>

\section{Model Order Reduction} \label{sec:3}
In this section we first explain the main results of \cite{Peng:2014di} regarding model reduction of Hamiltonian systems. In section ?? we introduce the model reduction of dissipative Hamiltonian systems.

@@

\subsection{The Reduced Dissipative Hamiltonian Method}

@@

\begin{algorithm}
\caption{The Reduced Dissipative Hamiltonian Method (RDH)} \label{alg:3.1}
\begin{enumerate}
	\item Construct the Hamiltonian extension (\ref{eq:2.10.a})-(\ref{eq:2.10.c}) to the original TDD system (\ref{eq:2.4}).
	\item Collect the snapshots $z(t_i)$, $i=1,\dots,N$ through time integration of the extended Hamiltonian.
	\item Construct an ortho-symplectic basis $A$.
	\item Define $\tilde L = A^T L A$, $\tilde \chi = A^T \chi A$ and construct the reduced dissipative Hamiltonian system (\ref{eq:3.12.a})-(\ref{eq:3.12.c})
\end{enumerate}
\end{algorithm}

### 2017-03-18 dissipative_hamiltonian/chapters/4.numer.tex
introduction added

\section{Numerical Results}
In this section we illustrate the performance of the discussed metthod through numerical solution of the dissipative wave equation and a port-Hamiltonian model for a dissipative circuit.

>>>>

\section{Numerical Results} \label{sec:4}
In this section we illustrate the performance of the discussed metthod through numerical solution of the dissipative wave equation and a port-Hamiltonian model for a dissipative circuit.
